---
title: "Cabbages"
author: "Stephanie Bolanos"
date: "Summer 2022"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  
$H_0$:There is not difference between the vitamin C content based on the cultivation methods of c39 and c52. 


$H_A$:There is a difference between the vitamin C content based on the cultivation methods of c39 and c52.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
We are explaining a vitamin c numerical variable by examining the categorical variable cultivation. We will use the T test to compare the mean of the two vitamin c groups. 

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results
```{r}
boxplot(VitC~Cult,data=veggy)
```

The category c39 for cultivating cabbages had an overall lower mean for the numerical result of the vitamin c. While the c52 category had a higher mean of the vitamin c using their cultivation method.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(VitC~Cult,data=veggy)
```
The cultivation method c39 had a median of 51.0, while c52 had a median of 64.5. C39 had a mean of 51.5 and c52 had a median of 64.4. Meaning that the cultivation method c52 was more successful in producing a higher average of vitamin c.


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```

Based on our two sample T test, we can infer that the P-value is 0.00000003405. From this we can reject the null hypothesis because the probability of the sample result was very unlikely, meaning that the null hypothesis is rejected. 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The difference between the two categories we had, cultivation methods c39 and c52 were found to have a numerical difference in the vitamin c produced in the cabbages made. We rejected the null hypothesis after seeing the results of the T test. The c39 had a mean of 51.5 while the c52 group had a mean of 64.5. The p-value from this test was 0.00000003405.
